The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-10 paper/ms.tex
Update end of intro

Underlying the quantitative analysis of many of the mechanisms at work that
give rise to these signatures is the assumption of a global, axisymmetric
Galactocentric coordinate system \citep{2008gady.book.....B} in which the
Sun's position (and therefore the origin of the coordinate system) can be
defined and measured both precisely and accurately. This involves measuring
the angular position of and distance to the Galactic center, the orientation
of the Galactic plane, the height of the Sun above the Galactic midplane, and
the local standard of rest (LSR). We review the observational efforts to
measure these parameters in Section~\ref{sec:mes_err}.

@@

In Section~\ref{sec:ref_frame}, we describe the general impact coordinate
system errors have on the measured actions. We then discuss two potential
sources of these coordinate system offsets in
Sections~\ref{sec:mes_err}~and~\ref{sec:local_fire}. In
Section~\ref{sec:mes_err} we discuss the potential errors in measuring the
parameters of the Galactocentric coordinate system. In
Section~\ref{sec:local_fire} we examine the azimuthal variations of the
midplane itself in two sets of simulations: cosmological, hydrodynamical,
zoom-in simulations of Milky Way-mass galaxies from the Feedback in Realistic
Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}}
\citep{2014MNRAS.445..581H, 2016ApJ...827L..23W, 2018MNRAS.480..800H}, and a
controlled N-body simulation of a Sagittarius encounter with a galaxy
otherwise tailored to the stellar mass, scale length, and scale height of the
Milky Way \citep{2018MNRAS.481..286L}.

>>>>

Underlying the quantitative analysis of many of the mechanisms at work that
give rise to these signatures is the assumption of a global, axisymmetric
Galactocentric coordinate system \citep{2008gady.book.....B} in which the
Sun's position (and therefore the origin of the coordinate system) can be
defined and measured both precisely and accurately. This involves measuring
the angular position of and distance to the Galactic center, the orientation
of the Galactic plane, the height of the Sun above the Galactic midplane, and
the local standard of rest (LSR). We review the observational efforts to
measure these parameters in Section~\ref{ssec:coord_off}.

@@

In Section~\ref{sec:ref_frame}, we describe the general impact coordinate
system errors have on the measured actions. In
Section~\ref{sec:local_fire} we examine the azimuthal variations of the
midplane itself in two sets of simulations: cosmological, hydrodynamical,
zoom-in simulations of Milky Way-mass galaxies from the Feedback in Realistic
Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}}
\citep{2014MNRAS.445..581H, 2016ApJ...827L..23W, 2018MNRAS.480..800H}, and a
controlled N-body simulation of a Sagittarius encounter with a galaxy
otherwise tailored to the stellar mass, scale length, and scale height of the
Milky Way \citep{2018MNRAS.481..286L}.
